Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
replace fixed-word length by finite-word length, which is typically used in the control and DSP community

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour whereas the controller operates in 
discrete time and over a quantised domain.  
Inspired by a classical approach \cite{astrom1997computer}, 
we translate the problem into a single digital domain.  
Given our primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with fixed-word
length (FWL). 
\red{[acronym later defined as finite-word length - please unify use]} 
The deterministic effects of the FWL and
quantisation errors are incorporated into the model as an additive
uncertainty, which is taken into account during the CEGIS-based synthesis of
the control software for the plant.

>>>>

Our work addresses particularly challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model, where
the plant exhibits continuous behaviour whereas the controller operates in 
discrete time and over a quantised domain.  
Inspired by a classical approach \cite{astrom1997computer}, 
we translate the problem into a single digital domain.  
Given our primary interest in stability despite digitisation effects, we have modelled
a digital equivalent of the plant by evaluating the effects of the
quantisers (A/D and D/A converters) as time discretisation elements with
quantisation noise.  The resulting closed-loop system is a program loop that
operates on bit-vectors encoded using fixed-point arithmetic with finite-word
length (FWL). The deterministic effects of the FWL and
quantisation errors are incorporated into the model as an additive
uncertainty, which is taken into account during the CEGIS-based synthesis of
the control software for the plant.
